Comparison of FDR methods on GWAS with SummarizedBenchmark

### 2017-10-20 datasets/GWAS/GWAS-SummarizedBenchmark.Rmd
Update to use common bench design function

# wrangling & plotting tools
library(data.table)
library(readxl)
library(dplyr)
library(ggplot2)
library(magrittr)
library(R.utils)

@@

# comparison tools/functions
library(SummarizedBenchmark)
source("benchmark-fdr/simulation_studies/R/simulation-helpers.R")
sourceDirectory("benchmark-fdr/datasets/R/")
```

@@

First, we'll create an object of `BenchDesign` class to hold the data.

@@

```{r, GWAS1-benchdesign}
bd <- BenchDesign(bmi)
```

Next, we'll add the benchmark methods to the `BenchDesign` object.

```{r, GWAS1-methods}
# This should maybe be sourced from a common script that everyone uses...
bd %<>% addBMethod(blabel = "BH", bfunc = p.adjust,
                 p = pval, method = "BH")

bd %<>% addBMethod("qv", qvalue::qvalue,
                  p = pval,
                  bpost = function(x) { x$qvalues })

bd %<>% addBMethod("ihw", IHW::ihw,
                  pvalues = pval,
                  covariates = IHW::groups_by_filter(ind_covariate, 5),
                  alpha = 0.1,
                  bpost = IHW::adj_pvalues)
```

@@

```{r, GWAS1-sb}
resfile <- paste0(resdir, "bmi_summarizedBenchmark_",
                  nrow(bmi), ".RData")
if (!file.exists(resfile)){
  t1 <- proc.time()
  sb <- bd %>% buildBench
  metadata(sb)$data_download_link <- "http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip"
  save(sb, file=resfile)
  message(paste0("Took ", round((proc.time()-t1)[3],1),
                 " seconds for ", nrow(bmi), " SNPs."))
}else{
  load(resfile)
}

@@

```{r, GWAS1-plot, results="hide"}
## to go here - standardized plotting functions from SummarizedBenchmarks -
## to discuss at meeting 10/19

@@

```{r, GWAS1-cleanup}
rm(bmi)
rm(bmi_results)
```

>>>>

# wrangling & plotting tools
library(data.table)
library(readxl)
library(dplyr)
library(ggplot2)
library(magrittr)
library(R.utils)
library(cowplot)

@@

# comparison tools/functions
library(SummarizedBenchmark)
sourceDirectory("benchmark-fdr/datasets/R/")
```

@@

First, we'll create an object of `BenchDesign` class to hold the data and 
add the benchmark methods to the `BenchDesign` object.

@@

```{r, GWAS1-benchdesign}
bd <- initializeBenchDesign()
```

@@

```{r, GWAS1-sb, results="hide"}
resfile <- paste0(resdir, "bmi_summarizedBenchmark_",
                  nrow(bmi), ".RData")
if (!file.exists(resfile)){
  t1 <- proc.time()
  sb <- bd %>% buildBench(data=bmi)
  metadata(sb)$data_download_link <- "http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip"
  save(sb, file=resfile)
  message(paste0("Took ", round((proc.time()-t1)[3],1),
                 " seconds for ", nrow(bmi), " SNPs."))
}else{
  load(resfile)
}

@@

```{r, GWAS1-plot, results="hide"}
#

## to add here - standardized plotting functions from SummarizedBenchmarks -
## to discuss at meeting 10/19

@@

```{r, GWAS1-cleanup}
rm(bmi)
rm(bd)
rm(sb)
```
